Adopting agile in the large: motivations, success factors and challenges

### 2014-05-12 journal/article.tex
Work in progress

Primary sources listed various functions beyond development that are involved in
bringing products to the market. Marketing was a particularly frequently
mentioned group [P5, P17, P28, P31, P38, P45, P48]. Other groups involved in the
whole of product delivery were sales [P17, P31], infrastructure and operations
[P10, P45, P46, P50], user experience and design [P9, P10, P28], documentation
[P28], legal [P10], security [P10], customer services [P48], and finance [P48].
All of these groups were reported to be affected on some level by the agile
transformation.
% separate QA [P3], --> Later
% human resources --> Later

@@

@@

@@

"C: Adapting non-development parts of organization to agile"

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MARKETING NEEDS TO KNOW ON BEFOREHAND WHAT WILL BE RELEASED
% 
% 
% * Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
% * Problem: Sales and marketing organization had a different vision of the product
% * Problem: Product marketing was not collaborative, and in old mindset
% * Problem: Requirements --> user stories more granular and prioritized
% [P31]
% After several months of working on the new products, the Agile teams “drained”
% the backlog.   For a while, they kept busy working on new user stories that came
% directly from the strategic customer.  This began to lead to a disconnect
% between what the marketing and sales organizations believed to be the overall
% direction of the product, and the actual direction it was taking based on the
% needs of a single customer. It was clearly time for a regroup, and the
% engineering team pushed back on the MRD.  They were in full production mode
% using Agile and they needed more granular, prioritized user stories to fuel
% their efforts.  The teams needed product marketing to be more collaborative in
% the decomposition of the requirements. This was a totally foreign concept for
% the product marketing team. They had approached the relationship with
% engineering as a “black box” – high level requirements went in, and something
% eventually came out (usually late, and sometimes off the mark on what they
% expected).
% 
% 
% * Challenge: Accomodate time for export clearance
% * Challenge: Acquire third-party licensing authority --> prior to product release
% * Challenge: These processes will remain traditional
% * Challenge: Marketing needs some lead time
% * Enablement activities (sales materials, training)
% * These steps take time, but they are part of the product lifecycle
% * Challenge: Must know beforehand what will be in the product
% [P31]
% While changing our process in the front end of the value chain began to yield
% success, we discovered that there was also a traditional wall at the back end:
% our product release process.
% While the Agile approach enables teams to be flexible with regard to
% prioritization, and very adaptive to changing market conditions and customer
% needs, there are certain “laws of physics” required to release commercial
% product that cannot be altered. For example, the time required to acquire export
% clearance or to acquire third-party licensing authority prior to product
% release.  As a vendor that makes products that must be marketed, sold and
% implemented, there are several traditional processes that are involved in
% releasing our products to market.
% 
% First there are the regulatory requirements such as export compliance relative
% to exporting code with certain levels of encryption,  then there are the
% marketing launch plans (demand generation campaigns, collateral, Web site,
% public relations), and finally, the field enablement activities (sales
% materials, training).  All these initiatives take time, and they cannot begin
% without knowledge of exactly what is going to be in the product.
% 
% 
% * Problem: Marketing had to know on beforehand what will be in the release
% * Problem: Business went with requiring a fixed delivery date and a fixed feature set
% [P31]
% Serious friction arose. The development teams became frustrated because they
% felt marketing and the NPI process was stalling their progress and throwing up
% barriers against the core principles they had adopted.  Marketing, who needed to
% begin prepping for the launch of the product about three months before the
% actual date, found themselves struggling to message and develop materials and
% campaigns without a clear understanding of the features and functionality that
% would actually be “ready” on the release date. And, the NPI group could not
% apply for export compliance nor could they request any third party license
% authorization without knowing what was actually going to be in the product.
% 
% 
% * Solution: Development and product marketing work together
% * Solution: Product marketing can require a release to be completed in 90 days
% [P31]
% What we instituted was what we call an “Iron Triangle.” The concept is that at
% some number of sprints out before a release, we would commit to delivering a
% fixed set of features and functionality  at a certain date.  Of course, there
% was always the opportunity for us to deliver more than what we committed to, 
% but we absolutely had to deliver the set features by the set date.
% 
% If  product marketing wants to release product for any reason they can “declare”
% a release date, and  we’re able to lock the current feature set and have  the
% code ready to release within two sprints of the date they declare the release
% necessary.

@@

REQUIREMENT AND MRD COMMUNICATION PROBLEMS

* Not agile: MRDs --> Stories had to be extracted from detailed documentation --> Not good
* MRDs not based on reality
[P2]
Extracting user stories from existing, very detailed ‘marketing requirements
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact
found across the organisation. Leaders of Project Z claimed that it was very
difficult to work with such detailed documents in a project whose scope could
change rapidly; one agile developer described MRDs as “not based in reality at
all”.
Comment:
The problem with MRDs is a symptom of the challenge to integrate "the business" with the agile process.

* Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
* Problem: Sales and marketing organization had a different vision of the product
* Problem: Product marketing was not collaborative, and in old mindset
* Problem: Requirements --> user stories more granular and prioritized
[P31]

* Requirements engineering must be done differently
[P45]
Product teams had to communicate with business management, marketing, and field
services who were not fully prepared for how Scrum and the product teams’
expectations would change their daily work. The process of software requirements
engineering were found to require a major adjustment.

>>>>

Primary sources listed various functions beyond development that are involved in
bringing products to the market. Marketing was a particularly frequently
mentioned group [P5, P17, P28, P31, P38, P45, P48]. Other groups involved in the
whole of product delivery were sales [P17, P31], infrastructure and operations
[P10, P45, P46, P50], user experience and design [P9, P10, P28], documentation
[P28], legal [P10], security [P10], customer services [P48], and finance [P48].
All of these groups were reported to be affected on some level by the agile
transformation.

@@

% This where?

@@

% Requirements engineering is difficult

Point --> Requirements management also needs to adopt the new methodology
Product management was initially done in a traditional way, but it was not
capable of iteratively supplying small enough requirements to the agile
development process [P51]. The agile method had to be extended to include a
process on how to get large requirements into team backlogs [P31].

And --> The methodology needs to be adjusted
Scrum had to be adjusted to fit for large scale development, as the methodology
did not have guidelines on how to large and complex requirements [P31, P51].

In agile methods requirements engineering is usually a task closely tied to the
development team. However, large development projects will demand more
requirements management effort.
This is apparent in cases where complexity of the product will require
additional layers of product management [P45], requirements are created by
several stakehoder groups and development teams can not be in contact with all
of them [P39], or teams do not have access to stakeholders due to a distributed
seetting [P24].

In the development life cycle requirements were in some cases first defined on a
high level in marketing requirements documents (MRD) [P1, P31] or functional
specifications [P33]. The high level requirements needed to be elaborated to be
used by development teams. The requirements breakdown in it self was found to be
difficult [P1, P33], and also when to do the breakdown to which detail level
[P17].

Several cases described that much learning was needed to master the new process
of creating user stories, both on product management and development levels
[P11, P27, P30, P33, P37]. Also the effort estimation for stories was hard to do
well [P27, P37].

Product managers and business analysts were struggling in creating high level
requirements [P33, P37], and teams were struggling in breaking them down to an
estimable size [P33]. Smits and Rilliet [P48] describe how high level product
management delivered requirements in too large chunks resulting in development
teams spending large amounts of time on defining suitaby sized stories.

Some cases reported  Some organizations used a quality assurance group separate
from development.

@@

LARGE SCALE DEVELOPMENT EFFORT WILL DEMAND MORE FROM REQUIREMENTS MANAGEMENT
[P17]
% [P31] --> Scrum needs adjustment [P51b]
% [P39] --> All subject matter experts can not be brought together
[P46] --> High level stakeholders must be connected at project start
[P45] --> Communicating requirements down
[P51b] -> Non agile requirements management
  |
  v
BREAKDOWN IS HARD IN LARGE SCALE
[P1]  --> Extracting from MRDs hard (in general)
[P17] --> Have correct granularity at each phase in the life cycle
[P33] --> Breaking down backlogs was really hard
[P37] --> Business analysts not used to breaking down
[P48] --> Too large requirements to teams
[P51b] ->

THERE IS A GAP BETWEEN HIGH LEVEL AND DEVELOPMENT
[P31] --> Product marketing team was not collaborative at start (product managers)
[P39] --> Requirements are gathered in a separate function
[P45]

PROBLEMS IN REQUIREMENTS DEFINITION BEGINNING
[P31]
[P46]

CUSTOMERS NOT AVAILABLE
% [P39]

GENERAL AGILE PROBLEM
[P5]  --> Requirements defined ambiguously

BAD BEHAVIORS IN REQUIREMENTS MANAGEMENT
[P31] --> Backlog bartering
[P31] --> Teams listened to single customer instead of big picture set by product marketing team

CREATING USER STORIES WAS GENERALLY HARD TO LEARN

* Writing user stories was difficult at start --> It was hard to learn the breakdown practice
* Hard to do well in sprint planning session
[P11]
Writing and grooming user stories seems like a simple process during Scrum
training.  When many teams start sprinting at once, no one starts off as an
expert at writing stories.  In the mad rush to convert requirements to stories,
many stories had the correct format, but were often too big, too ambiguous, or
too prescriptive.  Product owners and teams who held grooming sessions once or
twice a week over time refined their backlogs so that planning meetings were
short, and there was no wasted time between sprints trying to figure out what to
do next.  For one untended product backlog, we instituted “speed grooming” where
we spent a maximum of five minutes discussing a story to categorize it as “ready
for a team,” “obsolete,” “more grooming,” etc., so the stories could be readied
for upcoming sprints.  Most of our stories were for system software, not end
user features, so teams consistently underestimated how long a story would take,
and would complain that it couldn’t be broken down further.  All of sudden they
were being required to break down work that used to take months into tasks of a
few hours.  In hindsight, we could have reduced stress on everyone if we had
devoted more time upfront to developing everyone’s skills in writing stories and
decomposing epics.

* In the beginning the team had problems learning how to break down requirements into stories
* Solution: Better customer and team collaboration --> More real customer, less internal customer
[P27]
The team had difficulty estimating tasks during the planning session: What
should go into a story? How should a task card be written? Is the story points
system better than the hour’s system? We also had a lack of well-defined
acceptance criteria before and during the planning session.

One solution we came up with was to improve the relationship between us and our
internal customers. Planning sessions were dreaded - long and not well
structured. Our team was driven based on the internal customer requirements,
which went into a backlog that the program manager also known as Susha
maintained. The more efficient way to understand what a task entailed was to
involve the customers in our planning meeting and pair up with them on writing
the actual story. The customers partnered up with us for 15 minutes during the
planning sessions.

* Agile raised awareness of requirements churn
* Completed stories did not always add value for clients --> Stories defined badly
* Problem: There was a separation between development teams and customers
[P30]
The introduction of Agile raised visibility of the requirements churn and lack
of clarity in feature definition, but writing good user stories remained
difficult, due in part to the separation between the client and product
development teams. Engineering became known as the “story-eating engine.”
Stories were being completed, but did not always add value for clients.
Agile successfully exposed the next areas needing attention: defining
value-added stories.

* The shift in practice from functional specs to user stories is challenging
[P33]
The transition from writing full product or functional specs to writing user
stories is challenging. Learn how to break up larger features into smaller user
stories, and prioritize them.

* Business analysts have problems with stories
* No skills in requirements breakdown
* Story breakdown was difficult practice --> Teams
* Things got better with time
[P37]
Our business analysts were running into the same issue one level up. They were
not used to providing feature requirements in story form, much less breaking
down these ”feature” level stories into stories that could be reasonably
estimated by the development team. I realized almost immediately the stories
were too big, but you can’t force immediate understanding. Like any skill,
estimating takes practice. We went through many agonizing estimation and story
breakdown sessions before we started to get some traction. As we began to build
up some historical data this closed the feedback loop. The team was able to see
that we were frequently underestimating and that this was directly connected to
the trouble we were still having with story breakdown.

We started finishing cards, but found that estimates of hours often took weeks.
Stories would spawn additional stories in order to reach completion. For
example, a story that started with a two day estimate would generate a week’s
worth of stories (sometimes even more than a week!). Many agile developers would
say ”Great! That’s part of agile.” Gaining clarity on a story and understanding
that there is more to it is part of the process. Unfortunately this was
happening far too often.

"C: Difficulties with requirements engineering or backlog"

* Not agile: MRDs --> Stories had to be extracted from detailed documentation --> Not good
* MRDs not based on reality
* Extracting user stories from MRDs --> Breakdown hard because of too much detail in MRDs
[P1, P2]
Extracting user stories from existing, very detailed ‘marketing requirements
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact
found across the organisation. Leaders of Project Z claimed that it was very
difficult to work with such detailed documents in a project whose scope could
change rapidly; one agile developer described MRDs as “not based in reality at
all”.
Comment:
The problem with MRDs is a symptom of the challenge to integrate "the business" with the agile process.

* The requirements were vaguely defined in the beginning --> Abmbiguity in requiements
* There was no extended QA period when requirements ambiguities were resolved in the old model
* Connection to QA
* Solution: better requirements management
* Solution: New role to bridge gap between high and detailed level
* Solution: Requirements are elaborated JIT
* Solution: Requirements runway [P17]
[P5, P17]
There was constant debate over both the meaning of the requirement and whether
or not the requirement was met.  Quality Assurance engineers were frustrated
trying to determine whether or not we should accept this feature.  Simply put,
we had not invested enough of our velocity in either up front or ongoing
requirements elaboration.
Going into the second release, we knew we had to do a better job with managing,
elaborating, and prioritizing requirements.  This had strictly been an issue
regarding where we chose to invest our energy.
Properly managing requirements was critical.

* The scale of the enterprise did not allow for ``throw away stories''
* Problem: Scale/size demands better requirements management 
[P17]
As BMC went through their initial iterations, they realized there was often a
gap between the level of detail in their system level features and the detail
needed for iteration planning and execution. The use of simple “throw away
stories” was insufficient to their challenge of scale. To bridge this gap, BMC
created the role of Requirements Architect as part of each development team.
The responsibility of each Requirements Architect is to take the high-level
features defined by product management and decompose these on a just-in-time
basis into the more detailed requirements and stories needed to drive iteration
planning and development.
This new role increased the accuracy of development estimates and improved the
collaboration between the development team and product management.

* Problem: Correct granularity in requirements at each stage in the life cycle
[P17]
One of the challenges BMC faces is defining the right level of requirement
detail at the right time in the life cycle. BMC is now using Rally Software to
manage a prioritized feature backlog and to elaborate the requirements and
stories for each component that will likely be needed to implement the feature.

* High level requirements are problematic
[P30]
Continuing progress includes:
* Managing an effective enterprise backlog.

* Large scale requires adjustment to Scrum practices --> Requirements --> Getting things in backlog
* Enterprise QA
[P31]
we discovered some areas that would require us to adapt our chosen Scrum
methodology to account for the realities of complex, large-scale development. 
Two key activities fell outside the scope of our original Scrum framework
1. Informing how things get into the backlog, and 2. Enterprise testing.

* The agile setup allowed for change --> Backlogs could be changed at beginning of each sprint
* Backlog bartering --> Negative effects --> Distrust
* Collaboration between product marketing and development to manage requirements
[P31]
Once the organization began to understand the increased productivity of the
Agile teams, and they saw that every three weeks the teams selected what they
would work on, they began to grasp the possibility that any feature request
could be delivered in mere weeks.
And, suddenly, we found the backlog was “up for grabs” at the beginning of each
sprint.
Requests came flooding in from the field, from marketing, from our support
organization. They would be automatically added to the backlog, and each sprint
became an opportunity to evaluate and reprioritize.
And, since the Agile approach increases collaboration, everyone had the
opportunity to “lobby” for his or her requests to make the backlog. This
constant influx of demand from several sources began to put a strain on the
system.  Questions about how to prioritize the backlog items and a subversive
process of “backlog bartering” began. This negatively impacted the teams and
their performance, and it also generated distrust among the various groups.

* Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
* Problem: Sales and marketing organization had a different vision of the product
* Problem: Product marketing was not collaborative, and in old mindset
* Problem: Requirements --> user stories more granular and prioritized
[P31]
After several months of working on the new products, the Agile teams “drained”
the backlog.   For a while, they kept busy working on new user stories that came
directly from the strategic customer.  This began to lead to a disconnect
between what the marketing and sales organizations believed to be the overall
direction of the product, and the actual direction it was taking based on the
needs of a single customer.
It was clearly time for a regroup, and the engineering team pushed back on the
MRD.  They were in full production mode using Agile and they needed more
granular, prioritized user stories to fuel their efforts.  The teams needed
product marketing to be more collaborative in the decomposition of the
requirements. This was a totally foreign concept for the product marketing team.
 They had approached the relationship with engineering as a “black box” –
highlevel requirements went in, and something eventually came out (usually late,
and sometimes off the mark on what they expected).

* Backlog management was difficult
* Requirements breakdown was very difficult
* Teams did not have insight on how to organize backlogs across teams
* Inconsistency of backlog management practice between teams
[P33]
In addition to the hottest ideas coming off the IdeaExchange, salesforce.com’s
product managers also have backlogs of important features, and these product
backlogs are an integral part of ADM.
The initial creation and prioritization of product backlogs was an ominous
challenge, and nearly impossible to achieve in the two-month timeframe the
product managers were allotted. Breaking down requirements into both epic and
detailed user stories was arduous, and the way in which the requirements were
broken down was inconsistent between teams because each team had limited insight
into how other teams were organizing their product backlogs.
To address this issue, salesforce.com built an in-house app called  Scrumforce

* Challenge: Writing user stories is hard
* The shift in practice from functional specs to user stories is challenging
* User stories should be written complete and accurately --> in the beginning of the sprint
* (no further mentionings of large scale)
[P33]
The transition from writing full product or functional specs to writing user
stories is challenging. Learn how to break up larger features into smaller user
stories, and prioritize them.

With user stories come smaller and more vague requirements, and because of the
agile nature of the development process, the product owner has a tendency to
change requirements during a sprint. Often, this is due to the product owner not
specifying the full requirements before the sprint starts. This can waste time
and result in work that is thrown away. User stories should be complete, have
acceptance criteria, and be usability tested before being added to a sprint.
Having clear guidelines prepared for when the team is ready to tackle a user
story will help reduce waste.

* Requirement management was difficult
* Actual stakeholders were not available for teams 
[P39]
there were a number of difficulties in requirements management. Actual
stakeholders weren’t available for the teams due to  many reasons and they used
another consulting company in the UK to gather their requirements, design UI and
communicate them back to teams. Even more requirements were provided from risk
management subject matter experts in London.
Comment: This sounds a bit like the initial state.

* Large scale problem
* It is impossible to bring all subject matters together in a large project
[P39]
Product discovery workshops are an extremely efficient technique allowing for
quick elaboration of a product roadmap and creating mid-term requirements
details. However, as most efficient tools do, it has certain limitations. One of
them is the need to have the PO and the team co-located for a sprint which might
be a budget issue for a distributed project. Another one is the nature of a PO
role in enterprise projects where you simply can’t bring all the subject matter
experts in one place with the team for any reasonable amount of time.

* Product management unable to communicate requirements down to development
* High level design functions had hard time communicating together and with development
[P45]
Around the same time some problems surfaced which were not connected to Scrum
usage but needed to be resolved before moving to Scrum on a large scale:
1. Communication among product management, software architects, development
   teams, and quality assurance was not strong enough to ensure a common
   understanding of development goals. Product management often was unable to
   communicate product requirements to software engineers. Languages and
   notations differed significantly.
2. The role of software architecture (high-level design) was not yet well
   understood. This led to increased dependencies among products and components,
   e.g. because componentization was weak and code reuse was highly valued.
   Another result was the lack of conceptual preparation for the development
   teams for whom there were too many obstacles to harmonize on interfaces and
   adhere to delivery timelines.
To overcome both problems a team was formed to provide education on software
architecture for developers, software architects, and product management.

* Requirements engineering must be done differently
* Product management has a hard time managing many agile teams simultaneously
[P45]
Upscaling methods were mainly driven by theoretical considerations. Implementing
them revealed that the skills and knowledge of product managers and software
architects were often not sufficient to manage a number of Scrum teams
concurrently. Product teams had to communicate with business management,
marketing, and field services who were not fully prepared for how Scrum and the
product teams’ expectations would change their daily work. The process of
software requirements engineering were found to require a major adjustment.

* Backlog could not be managed sensibly for teams over 130 people
* Product management with a too large scope did not work
* Managing requirements for product backlog is difficult in large scale (generally)
* Hierarchial requirements management is troublesome
* The organization's hierachy is reflected in requirements management
[P45]
A three-level hierarchy of teams to manage requirements for product backlog
generation has not yet proven to work as expected. Currently the high complexity
of SAP’s products which is reflected in the organizational structure of SAP’s
development areas makes it impossible to drop one hierarchy level of project
management. This observation has triggered significant effort to rigorously
break up SAP’s product lines into separate components to ensure that no product
component needs more resources than the 130 people as calculated above.

* Problems with backlogs at project start --> inconsistency at project start
* Product management (PO) tasks have to be done at project start
* Technology and business leadership (high level) needs to be engaged strongly at project start
[P46]
After month 16 of our journey, focus shifted toward connecting the product
owners, Scrum Masters and technology managers prior to the project start. Our
projects were starting without good backlogs and the level of product owner
involvement was inconsistent, causing projects to start slowly. After some soul
searching we concluded that we were treating agile development as a paradigm
shift (mapping existing roles to Scrum roles, yet not doing anything different).
What we needed was to educate it as a new paradigm. The result was Agile
Connections. This is a sequence of training that starts with an overview to
create awareness and desire to use agile practices in delivering the business
value. Then, hands-on workshops transfer knowledge, followed by jump starts and
coaching to help reinforce the ability to use the practices. The overall goal is
to get the product owner, ScrumMaster and technology manager together to enable
projects to start better.

* Too large requirements to teams --> Could not break down stories
* Difficulties in breaking down requirements to stories
* Business (high level) requirements management gave too large chunks of requirements to development
[P48]
An executive Portfolio Investment Committee was initiated with the goal of
working across all of the business units in our Technology Group to set
investment priorities. Two problems emerged – we did not have the management
information to support the decisions of the Portfolio Committee, and information
about the strategic decisions and direction were not effectively communicated to
the organization so that all participants in the system release planning process
were informed. The next stage of “decomposition” of Themes, Epics and User
Stories didn’t really happen, so that the chunks of work were so large that the
Product Teams and Scrum teams had to spend an inordinate amount of time breaking
things down, (and clarifying the requirements at the lower levels) before any
sprint zero or sprint planning could occur.

* Sprint planning was taking too long --> User story breakdown was too difficult
* Solution: Story estimation is done more iteratively
[P51] (Case A)
The sprint planning meeting initially took approximately one day, because all
the user stories had to be discussed, estimated and planned at once. This was
considered too long to be effective. Therefore, story estimation is now done
regularly throughout the sprints. This requires shorter bursts of attention,
which eases the process. On the day of the sprint planning, the product owners
present the user stories to their own team(s), followed by the selection and
planning of user stories by the development teams. The process of selection and
planning now takes approximately one hour, instead of one day.

* Requirements given from product management too large --> not enough detail for development
* Product management adapted to Scrum --> Continuous attention to product backlog
* Scrum does not tell how to manage large requirements on different levels 
[P51] (Case B)
Until 2007, agile product development was accompanied by non-agile product
management. Although several stages of elaboration were employed, no fixed
cycles were used. This caused that product managers did not manage to provide
development with sufficiently detailed requirements before the start of each
sprint. To improve this, the product management team adjusted their process to
the Scrum principles as well. This implied a continuous adaptation of the
product backlog to a changing environment. Since Scrum itself does not provide
guidelines for effectively managing large amounts of requirements of different
granularity, a set of stages has been introduced, called the Agile Requirements
Refinery [26]. Within the agile requirements refinery, an idea will generally
move through the stages vision, theme, concept, and requirement definition.
During these stages, requirements are refined with details and specifications.
This has resulted in a new categorization on the product backlog.

MULTISITE CASE

% * Requirements engineerinf was difficult in Multisite
% [P24]
% Initially we started with the Product Owner (PO) as a role for sales and account
% management. It worked reasonably well with local teams in Denmark when they
% could collaborate and meet when required. But it did not work well with teams in
% Bangladesh. We moved some of the very experienced senior developers and
% consultants into global PO roles to establish a more structured flow of tasks
% and collaboration with the teams. To establish a structure to improve the flow
% of work between the Danish and the Bangladeshi teams we introduced a “Proxy PO”
% for each team in Bangladesh.
% 
% Understanding the problem domain and how the different requirements were related
% was still hard. We used many different techniques to move the domain knowledge
% and user understanding out to the different teams.
% 
% 
% * Solution: Global planning is required for multisite
% [P24]
% Global planning:
% Having one team and therefore one sprint backlog meant, that we had to do sprint
% planning together. Not an easy task, but after some experiments, we came up with
% a solution that worked for us:
% 
% • The whole global team was presented with the user stories online
% • The global team went offline and started to break down the stories and meet to
%   synchronize sprint backlog items into one sprint backlog
% • The global team informed the PO of the result
% 
% We spent a lot of time trying to make it work well, and it required a high level
% of trust between all parties. It also required a lot of knowledge of the
% business domain, but made it easy to ask for the relevant knowledge when doing
% the breakdown and planning.
% 
% 
% * Colocation of requirements communication is required even in multisite  
% [P24]
% The R\&D team could build the best quality code, but we kept building elements
% of the wrong things. It was almost like building a top of the line V12 engine, for
% a solar cell car race. The trust between the team and the PO were at stake. “I
% told you to build an engine, and you should have known it was an electric engine
% I needed”. So once again we had to improve the quality and understanding of
% requirements between the PO and the global team both before and during the
% actual development in the sprint. After retrospectives and more discussions, we
% decided to try moving the PO into the Danish R\&D team room.

@@
